%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------------------------------------RESUME STARTS------------------------------------------------

%----------HEADING----------

\begin{center}
    \textbf{\Huge \scshape Vishesh Kumar Dubey} \\ \vspace{1pt}
    \small +91 88402 24036 $|$ \href{mailto:visheshdubey2016@gmail.com}{\underline{visheshdubey2016@gmail.com}} $|$ 
    \href{https://github.com/visheshdubey}{\underline{github.com/visheshdubey}} $|$  \href{https:visheshdubey.com}{\underline{visheshdubey.com}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Uttaranchal Institute of Technology (8.2 CGPA)}{Dehradun, India}
      {Bachelor of Technology in Computer Science}{Aug. 2017 -- June 2021}
    \resumeSubheading
      {St. Josephs School}{Gorakhpur, India}
      {Intermediate - Maths \& Computer Science}{April. 2015 -- May 2016}
  \resumeSubHeadingListEnd

%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Java, JavaScript, Typescript, C\#, Python, SQL (Postgres),  HTML/CSS} \\
     \textbf{Frameworks}{: React.js, Next.js, React Native, Express.js, Node.js, TailwindCSS, Strapi.Js,  framer motion,  Radix UI, Chakra UI } \\
     \textbf{Developer Tools}{: Git, Docker,  Prisma(ORM), husky, Firebase, Azure Cloud, Azure Server-less functions, VS Code, Visual Studio, Notion, Figma, Eclipse} \\
     \textbf{Libraries}{: RTK Query, bcrypt, zod, react-hook-form, React Tables }
    }}
 \end{itemize}


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Software Engineer}{Feb 2022 -- Present}
      {Accenture}{Bangalore, India}
      \resumeItemListStart
        \resumeItem{Designed, Build, tested and deployed Azure function Apps, Azure Data Factory, Logic apps using Azure CI/CD Pipelines}
        \resumeItem{Worked on developing Jump Server to connect to SFTP servers using Azure Web Apps, .NET and Bootstrap 5.0}
        \resumeItem{Worked with various Azure Cloud technologies such as Serverless Function Apps, Storage accounts, Azure Datalakes, Service Bus/Event Hub triggered function apps.}
      \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------



%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{OpenHiring} $|$ \emph{Next.Js, Typescript, TailwindCSS, Radix UI, AuthJS, Vercel, Git, }}{June 2023 -- July 2023}
          
          \resumeItemListStart
            \resumeItem{Developed a full-stack job portal using \textbf{Next.js, TypeScript,} and Azure Function Apps.}
            \resumeItem{Integrated \textbf{OPEN AI API (ChatGPT)} to extract job details like title, company, and salary from \textbf{Hacker News postings.}}
            \resumeItem{Implemented a user-friendly UI with \textbf{Tailwind CSS} and deployed the project on Vercel.}
            \resumeItem{Secured user access with Google and email/password authentication using \textbf{auth.js}.}
            \resumeItem{Demonstrated proficiency in front-end and back-end development while leveraging AI-powered APIs for automation.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{TRNR} $|$ \emph{ReactNative, Javascript, StrapiJS, AWS EC2 \& S3, Git}}{Sep 2022 -- Jan 2023}
          
          \resumeItemListStart
            \resumeItem{Developed a cross-platform educational app using \textbf{React Native} and \textbf{Expo,} catering to fitness enthusiasts.}
            \resumeItem{The app featured 300+ products with detailed workout guides and instructional videos for proper exercise techniques.}
            \resumeItem{Leveraged AWS S3 to efficiently store and stream over 1000 high-quality video assets within the app.}
            \resumeItem{Implemented a robust backend using \textbf{Strapi.js} and custom APIs to manage user authentication, account creation, and favorite workout bookmarking.}
             \resumeItem{Deployed the backend on AWS EC2, ensuring smooth app performance and seamless access to educational resources for users.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Certifications}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Microsoft} $|$ \emph{AZ-900 }}{June 2022}
          
          \resumeItemListStart
            \resumeItem{Cloud computing fundamentals, deployment models, and service categories.}
            \resumeItem{Overview of Microsoft Azure services and solutions like VMs, storage, and Azure AD.}
          \resumeItemListEnd
\resumeSubHeadingListEnd
%